\begin{thebibliography}{99}

\bibitem{1} M. Barni et al., ``Information Forensics and Security: A quarter-century-long journey,'' \textit{IEEE Transactions on Information Forensics and Security}, vol. 19, pp. 2856--2893, 2024.
\bibitem{2} M. Alazab et al., ``Enhanced threat intelligence framework for advanced cybersecurity resilience,'' \textit{Egyptian Informatics Journal}, vol. 27, art. 100521, 2024.
\bibitem{3} A. S. Alqahtani, ``Security threats and countermeasures in software defined network using efficient and secure trusted routing mechanism,'' \textit{Computer Networks}, vol. 177, pp. 102--115, Mar. 2020.
\bibitem{4} F. Alghamdi, ``A Comprehensive Investigation of Reconnaissance Threats in Cybersecurity,'' \textit{International Journal of Advanced Research in Management and Social Sciences}, vol. 13, no. 11, Nov. 2024.
\bibitem{5} X. Qin et al., ``A hybrid cyber defense framework for reconnaissance attacks in 5G networks,'' \textit{Computers \& Security}, vol. 136, art. 103569, 2024.
\bibitem{6} Z. Dong et al., ``Network measurement based modeling and optimization for IP geolocation,'' \textit{Computer Networks}, vol. 56, no. 1, pp. 85--98, Jan. 2012.
\bibitem{7} A. Hong et al., ``A Cheap and Accurate Delay-Based IP Geolocation Method using Machine Learning and Looking Glass,'' in \textit{Proc. IEEE INFOCOM Workshops}, 2023.
\bibitem{8} X. Liu et al., ``Robust IP geolocation through the lens of uncertainty quantification,'' \textit{Computer Networks}, vol. 257, 2025.
\bibitem{9} M. Schopman, ``Validating the accuracy of the MaxMind GeoLite2 City database,'' Bachelor's thesis, Radboud University, 2021.
\bibitem{10} M. A. Ferrag et al., ``Deep learning for cyber security intrusion detection: Approaches, datasets, and comparative study,'' \textit{Journal of Network and Computer Applications}, vol. 50, pp. 41--65, Feb. 2019.
\bibitem{11} P.-C. Lin et al., ``Correlation of cyber threat intelligence with sightings for intelligence assessment and augmentation,'' \textit{Computer Networks}, vol. 229, art. 109751, Jun. 2023.
\bibitem{12} Z. Durumeric et al., ``Censys: A Map of Internet Hosts and Services,'' Technical Report, 2025.
\bibitem{13} ``A Multi-Functional Web Tool for Comprehensive Threat Intelligence and Risk Assessment,'' arXiv preprint arXiv:2412.03023, 2024.
\bibitem{14} F. Alghamdi, ``A Comparative Analysis of Network Enumeration Tools,'' \textit{Journal of Computer Security and Cybercrime Management}, 2024.
\bibitem{15} J. M. Pittman, ``A Comparative Analysis of Port Scanning Tool Efficacy,'' arXiv preprint arXiv:2303.11282, 2023.
\bibitem{16} ``A comprehensive survey on concept drift and feature selection in machine learning for cybersecurity,'' \textit{ScienceDirect}, 2024.
\bibitem{17} W. Mazurczyk et al., ``Cyber reconnaissance techniques,'' \textit{Communications of the ACM}, vol. 64, no. 3, 2021.
\bibitem{18} G. Ciavarrini et al., ``Accuracy limits through Cram\'er--Rao lower bound for IP geolocation,'' \textit{Computer Networks}, vol. 131, pp. 37--50, 2018.
\bibitem{19} ``A Machine Learning Approach for Detecting Cybersecurity Vulnerabilities,'' \textit{Knowledge-Based Systems}, 2025.
\bibitem{20} ``NIST Cybersecurity Framework 2.0,'' NIST, 2024.

\end{thebibliography}
