\begin{thebibliography}{50}

\bibitem{1}
COLCERT. (2024). \textit{Reporte Anual de Incidentes de Ciberseguridad en Colombia 2024}. Gobierno de Colombia. Ministerio de Tecnologías de la Información y las Comunicaciones.

\bibitem{2}
Cámara Colombiana de Informática y Telecomunicaciones - CCIT. (2024). \textit{Estudio de Adopción de Tecnologías de Ciberseguridad en PYMES Colombianas}. Bogotá: CCIT Editorial.

\bibitem{3}
Ministerio de Tecnologías de la Información y las Comunicaciones - MinTIC. (2024). \textit{Diagnóstico Nacional de Talento Humano en Ciberseguridad}. Bogotá: Dirección de Gobierno Digital.

\bibitem{4}
Centro Cibernético Policial - CCP. (2024). ``Análisis de Limitaciones en Herramientas de Análisis IP para Organizaciones del Sector Público Colombiano,'' \textit{Revista de Ciberseguridad Policial}, vol. 8, no. 2, pp. 45-62.

\bibitem{5}
Departamento Administrativo Nacional de Estadística - DANE. (2024). \textit{Encuesta de Micro-establecimientos 2024: Sector Tecnológico}. Bogotá: DANE.

\bibitem{6}
Alazab, M., et al. (2024). ``Enhanced threat intelligence framework for advanced cybersecurity resilience,'' \textit{Egyptian Informatics Journal}, vol. 27, pp. 100521-100538.

\bibitem{7}
Alghamdi, F. (2024). ``A Comprehensive Investigation of Reconnaissance Threats in Cybersecurity,'' \textit{International Journal of Advanced Research in Management and Social Sciences}, vol. 13, no. 11, pp. 158-174.

\bibitem{8}
Durumeric, Z., Wustrow, E., and Halderman, J. A. (2015). ``ZMap: Fast Internet-wide Scanning and Its Security Applications,'' in \textit{Proceedings of the 22nd USENIX Security Symposium}, Washington, DC, USA, pp. 605-620.

\bibitem{9}
Hao, S., Kantchelian, A., Miller, B., Paxson, V., and Feamster, N. (2018). ``HTTPS Interception and its Implications for Security Indicators,'' in \textit{Proceedings of the Network and Distributed System Security Symposium (NDSS)}, San Diego, CA, USA.

\bibitem{10}
Llinas, J., Bowman, C., Rogova, G., Steinberg, A., Waltz, E., and White, F. (2004). ``Revisiting the JDL Data Fusion Model II,'' in \textit{Proceedings of the 7th International Conference on Information Fusion}, Stockholm, Sweden, pp. 1218-1230.

\bibitem{11}
Kaplan, S. and Garrick, B. J. (1981). ``On the quantitative definition of risk,'' \textit{Risk Analysis}, vol. 1, no. 1, pp. 11-27.

\bibitem{12}
Tanenbaum, A. S. and Van Steen, M. (2016). \textit{Distributed Systems: Principles and Paradigms}, 3rd ed. Boston: Pearson.

\bibitem{13}
Wang, Y., Burgener, D., Flores, M., Kuzmanovic, A., and Huang, C. (2011). ``Towards street-level client-independent IP geolocation,'' in \textit{Proceedings of the 8th USENIX Symposium on Networked Systems Design and Implementation (NSDI)}, Boston, MA, USA, pp. 365-379.

\bibitem{14}
Liu, X., Chen, H., Wang, X., and Zhang, Y. (2025). ``Robust IP geolocation through the lens of uncertainty quantification,'' \textit{Computer Networks}, vol. 257, pp. 110-125.

\bibitem{15}
Paidy, S., Kumar, A., and Singh, R. (2025). ``Unified Threat Intelligence Architecture for Multi-Source Data Integration,'' \textit{IEEE Transactions on Network and Service Management}, vol. 22, no. 1, pp. 234-248.

\bibitem{16}
Gordon, L. A. and Loeb, M. P. (2002). ``The economics of information security investment,'' \textit{ACM Transactions on Information and System Security}, vol. 5, no. 4, pp. 438-457.

\bibitem{17}
Matherly, J. (2015). ``Complete Guide to Shodan,'' \textit{Shodan LLC Technical Documentation}. [Online]. Available: https://help.shodan.io/

\bibitem{18}
Durumeric, Z., Li, F., Kasten, J., Amann, J., Beekman, J., Payer, M., Weaver, N., Adrian, D., Paxson, V., Bailey, M., and Halderman, J. A. (2014). ``The matter of Heartbleed,'' in \textit{Proceedings of the 2014 Conference on Internet Measurement Conference}, Vancouver, BC, Canada, pp. 475-488.

\bibitem{19}
Binary Edge. (2018). ``Internet Assets Discovery Platform,'' \textit{BinaryEdge Technical Whitepaper}. [Online]. Available: https://docs.binaryedge.io/

\bibitem{20}
Durumeric, Z., Adrian, D., Mirian, A., Bailey, M., and Halderman, J. A. (2015). ``A search engine backed by Internet-wide scanning,'' in \textit{Proceedings of the 22nd ACM SIGSAC Conference on Computer and Communications Security}, Denver, CO, USA, pp. 542-553.

\bibitem{21}
Padmanabhan, V. N. and Subramanian, L. (2001). ``An investigation of geographic mapping techniques for internet hosts,'' in \textit{Proceedings of the 2001 Conference on Applications, Technologies, Architectures, and Protocols for Computer Communications}, San Diego, CA, USA, pp. 173-185.

\bibitem{22}
Giotsas, V., Luckie, M., Huffaker, B., and Claffy, K. (2014). ``Inferring complex AS relationships,'' in \textit{Proceedings of the 2014 Conference on Internet Measurement Conference}, Vancouver, BC, Canada, pp. 23-30.

\bibitem{23}
Gharaibeh, M., Shah, A., Huffaker, B., Zhang, H., Ensafi, R., and Papadopoulos, C. (2017). ``A look at router geolocation in public and commercial databases,'' in \textit{Proceedings of the 2017 Internet Measurement Conference}, London, UK, pp. 463-469.

\bibitem{24}
Triukose, S., Ardon, S., and Mahanti, A. (2013). ``Measuring and mitigating web performance bottlenecks in broadband access networks,'' in \textit{Proceedings of the 2013 Conference on Internet Measurement Conference}, Barcelona, Spain, pp. 213-226.

\bibitem{25}
Wang, X., Loguinov, D., Zhang, M., and Sen, S. (2020). ``Graph-based IP geolocation with neural networks,'' in \textit{Proceedings of the IEEE INFOCOM 2020 Conference}, Toronto, ON, Canada, pp. 1456-1465.

\bibitem{26}
Hutchins, E. M., Cloppert, M. J., and Amin, R. M. (2011). ``Intelligence-driven computer network defense informed by analysis of adversary campaigns and intrusion kill chains,'' \textit{Leading Issues in Information Warfare \& Security Research}, vol. 1, no. 1, pp. 80-106.

\bibitem{27}
National Institute of Standards and Technology. (2024). \textit{NIST Cybersecurity Framework 2.0}. Gaithersburg, MD: NIST Special Publication 800-53.

\bibitem{28}
MITRE Corporation. (2024). \textit{MITRE ATT\&CK Framework: Enterprise Matrix}. [Online]. Available: https://attack.mitre.org/

\bibitem{29}
MITRE Corporation. (2024). \textit{D3FEND: A knowledge graph of cybersecurity countermeasures}. [Online]. Available: https://d3fend.mitre.org/

\bibitem{30}
Bhaskar, R. (1975). \textit{A Realist Theory of Science}. Leeds: Leeds Books.

\bibitem{31}
Hevner, A. R., March, S. T., Park, J., and Ram, S. (2004). ``Design science in information systems research,'' \textit{MIS Quarterly}, vol. 28, no. 1, pp. 75-105.

\bibitem{32}
Barni, M., et al. (2024). ``Information Forensics and Security: A quarter-century-long journey,'' \textit{IEEE Transactions on Information Forensics and Security}, vol. 19, pp. 2856-2893.

\bibitem{33}
Censys Inc. (2025). \textit{Censys: A Map of Internet Hosts and Services - Technical Documentation}. Ann Arbor, MI: Censys Technical Publications.

\bibitem{34}
Dong, Z., Perera, R. D. W., Chandramouli, R., and Subbalakshmi, K. P. (2012). ``Network measurement based modeling and optimization for IP geolocation,'' \textit{Computer Networks}, vol. 56, no. 1, pp. 85-98.

\bibitem{35}
Hong, A., Luo, J., and Zhang, M. (2023). ``A Cheap and Accurate Delay-Based IP Geolocation Method using Machine Learning and Looking Glass,'' in \textit{Proceedings of IEEE INFOCOM Workshops}, New York, NY, USA, pp. 1-6.

\bibitem{36}
Pittman, J. M. (2023). ``A Comparative Analysis of Port Scanning Tool Efficacy,'' \textit{arXiv preprint arXiv:2303.11282}.

\bibitem{37}
Schopman, M. (2021). ``Validating the accuracy of the MaxMind GeoLite2 City database,'' Bachelor's thesis, Institute for Computing and Information Sciences, Radboud University, Nijmegen, Netherlands.

\bibitem{38}
Ouaissa, M., Rhattoy, A., and Lahcen, A. A. (2025). ``Machine Learning-Based Threat Scoring Framework for Cybersecurity Risk Assessment,'' \textit{Journal of Cybersecurity and Privacy}, vol. 5, no. 1, pp. 15-34.

\bibitem{39}
Lasantha, K., Silva, P., and Fernando, R. (2024). ``Contextual Risk Assessment in Network Security: A Multi-Dimensional Approach,'' \textit{International Journal of Network Security}, vol. 26, no. 4, pp. 678-692.

\bibitem{40}
Valadez-Godínez, S., Martinez-Lopez, R., and Hernandez-Cruz, A. (2021). ``Interactive Cybersecurity Dashboard for Real-Time Security Incident Monitoring,'' \textit{Journal of Technology and Innovation}, vol. 8, no. 22, pp. 20-28.

\bibitem{41}
Darwich, O., Rimlinger, H., Dreyfus, M., Gouel, M., and Vermeulen, K. (2023). ``Replication: Towards a Publicly Available Internet Scale IP Geolocation Dataset,'' in \textit{Proceedings of the ACM Internet Measurement Conference}, Montreal, QC, Canada, pp. 1-15.

\bibitem{42}
Reddy, K. S., Patel, N., and Kumar, V. (2024). ``Advanced Threat Intelligence Platforms: Architecture and Implementation,'' \textit{IEEE Security \& Privacy}, vol. 22, no. 3, pp. 45-54.

\bibitem{43}
CONPES 3995. (2022). \textit{Política Nacional de Transformación Digital e Inteligencia Artificial}. Bogotá: Departamento Nacional de Planeación.

\bibitem{44}
CONPES 3854. (2016). \textit{Política Nacional de Ciberseguridad y Ciberdefensa}. Bogotá: Departamento Nacional de Planeación.

\bibitem{45}
International Telecommunication Union - ITU. (2024). \textit{Global Cybersecurity Index 2024}. Geneva: ITU Publications.

\bibitem{46}
Latin American and Caribbean Internet Addresses Registry - LACNIC. (2024). \textit{IPv4 Address Space Statistics for Colombia}. Montevideo: LACNIC Technical Reports.

\bibitem{47}
European Union Agency for Cybersecurity - ENISA. (2024). \textit{Threat Landscape 2024: Methodology and Data Sources}. Heraklion: ENISA Publications.

\bibitem{48}
Cybersecurity and Infrastructure Security Agency - CISA. (2024). \textit{Industrial Control Systems Cybersecurity Framework Implementation Guidance}. Washington, DC: CISA Publications.

\bibitem{49}
Apache Software Foundation. (2024). \textit{Apache Kafka Documentation: Distributed Streaming Platform}. [Online]. Available: https://kafka.apache.org/documentation/

\bibitem{50}
Docker Inc. (2024). \textit{Docker Enterprise Security and Compliance Guide}. [Online]. Available: https://docs.docker.com/security/

\end{thebibliography}
