\begin{thebibliography}{15}
\bibitem{1}
M. Barni, P. Campisi, E. J. Delp, G. Doërr, J. Fridrich, N. Memon, F. Pérez-González, A. Rocha, L. Verdoliva, and M. Wu, ``Information Forensics and Security: A quarter-century-long journey,'' \textit{IEEE Transactions on Information Forensics and Security}, vol. 19, pp. 2856--2893, 2024.

\bibitem{2}
P.-C. Lin, W.-H. Hsu, Y.-D. Lin, R.-H. Hwang, H.-K. Wu, Y.-C. Lai, and C.-K. Chen, ``Correlation of cyber threat intelligence with sightings for intelligence assessment and augmentation,'' \textit{Computer Networks}, vol. 229, art. 109751, Jun. 2023.

\bibitem{3}
A. Saad Alqahtani, ``Security threats and countermeasures in software defined network using efficient and secure trusted routing mechanism,'' \textit{Computer Networks}, vol. 177, pp. 102--115, Mar. 2020.

\bibitem{4}
Z. Dong, R. D. W. Perera, R. Chandramouli, and K. P. Subbalakshmi, ``Network measurement based modeling and optimization for IP geolocation,'' \textit{Computer Networks}, vol. 56, no. 1, pp. 85--98, Jan. 2012.

\bibitem{5}
M. A. Ferrag, L. Maglaras, S. Moschoyiannis, and H. Janicke, ``Deep learning for cyber security intrusion detection: Approaches, datasets, and comparative study,'' \textit{Journal of Network and Computer Applications}, vol. 50, pp. 41--65, Feb. 2019.

\bibitem{6}
O. Darwich, H. Rimlinger, M. Dreyfus, M. Gouel, and K. Vermeulen, ``Replication: Towards a Publicly Available Internet Scale IP Geolocation Dataset,'' in \textit{Proc. ACM Internet Measurement Conference}, Montreal, Canada, Oct. 2023, pp. 1--15.

\bibitem{7}
X. Wang, Y. Chen, L. Zhang, and M. Liu, ``NeighborGeo: IP geolocation based on neighbors,'' \textit{Computer Networks}, vol. 249, art. 110536, Jun. 2025.

\bibitem{8}
X. Liu, J. Zhou, H. Wang, and S. Chen, ``Robust IP geolocation through the lens of uncertainty quantification,'' \textit{Computer Networks}, vol. 251, art. 110672, Aug. 2025.

\bibitem{9}
P. Paidy, ``Unified Threat Detection Platform with AI, SIEM, and XDR,'' \textit{International Journal of AI and Data Science in Machine Learning}, vol. 6, no. 1, pp. 111--125, Jan. 2025.

\bibitem{10}
M. Ouaissa, M. Ouaissa, Z. Nadifi, S. El Himer, Y. Al Masmoudi, and A. Kartit, ``A framework for cyber threat modeling and risk assessment in smart city environments,'' \textit{Frontiers in Computer Science}, vol. 7, art. 1647179, Jul. 2025.

\bibitem{11}
N. W. C. Lasantha, ``A Novel Framework for Real-Time IP Reputation Validation Using Artificial Intelligence,'' \textit{International Journal of Wireless and Microwave Technologies}, vol. 14, no. 2, pp. 1--15, Apr. 2024.

\bibitem{12}
Z. Li, Y. Wang, J. Chen, and X. Zhang, ``Measuring and classifying IP usage scenarios,'' \textit{Nature Communications}, vol. 15, art. 1832, Feb. 2024.

\bibitem{13}
I. K. Kwento, ``AI-Driven Threat Intelligence for Enterprise Cybersecurity,'' \textit{Journal of Next-Generation Research}, vol. 1, no. 4, pp. 1--12, May 2025.

\bibitem{14}
H. M. Reddy, ``A Unified Approach to Cybersecurity and Information Security Managing Both Within one Platform,'' \textit{International Journal of Innovative Research in Management and Social Sciences}, vol. 12, no. 1, pp. 1--17, Jan. 2024.

\bibitem{15}
S. Valadez-Godínez, R. Martinez-Lopez, and A. Hernandez-Cruz, ``Interactive Cybersecurity Dashboard for Real-Time Security Incident Monitoring,'' \textit{Journal of Technology and Innovation}, vol. 8, no. 22, pp. 20--28, Dec. 2021.

\bibitem{Hevner2004}
A. R. Hevner, S. T. March, J. Park, and S. Ram, ``Design Science in Information Systems Research,'' \textit{MIS Quarterly}, vol. 28, no. 1, pp. 75--105, Mar. 2004.

\bibitem{Peffers2007}
K. Peffers, T. Tuunanen, M. A. Rothenberger, and S. Chatterjee, ``A Design Science Research Methodology for Information Systems Research,'' \textit{Journal of Management Information Systems}, vol. 24, no. 3, pp. 45--77, Dec. 2007.

\bibitem{Winter2008}
R. Winter, ``Design science research in Europe,'' \textit{European Journal of Information Systems}, vol. 17, no. 5, pp. 470--475, Oct. 2008.

\bibitem{Wirth2000}
R. Wirth and J. Hipp, ``CRISP-DM: Towards a Standard Process Model for Data Mining,'' in \textit{Proc. 4th International Conference on the Practical Applications of Knowledge Discovery and Data Mining}, Manchester, UK, Apr. 2000, pp. 29--39.

\bibitem{Schroer2021}
C. Schröer, F. Kruse, and J. M. Gómez, ``A Systematic Literature Review on Applying CRISP-DM Process Model,'' \textit{Procedia Computer Science}, vol. 181, pp. 526--534, 2021.

\bibitem{Anderson2022}
P. Anderson and K. Smith, ``Applying CRISP-DM to Cybersecurity Data Analysis,'' \textit{Journal of Cybersecurity Research}, vol. 6, no. 2, pp. 78--92, Jun. 2022.
\end{thebibliography}
